Interval Probability for Fuzzy Quantum Theories

### 2016-07-21 prob.tex
prob.tex Keep updating and fight with BibLaTeX with LyX and TeXlipse >"<

\documentclass{article}
\usepackage[ backend=biber,sorting=none]{biblatex}
\addbibresource{discreteGBKS.bib}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

@@

\yutsung{A mathematical reason why Gleason's theorem should not be
valid in the interval-valued probability quantum mechanics. Every
classical probability measure has a one-to-one correspondence to its
Radon-Nikodym derivative. The Radon-Nikodym theorem extends to Gleason's
theorem in quantum, while the role of Radon-Nikodym derivative is
replaced by the density matrix. If there is no easy Radon-Nikodym
theorem for classical interval-valued probability measure (\cite{GilboaSchmeidler1994}
or other sources. Need verify!), it is natural that there is no easy
Gleason's theorem for quantum interval-valued probability measure...

@@

In previous section, the probability of each event is known
a priori. In reality, we seldom know much about events, but we could still assume
each event~$E$ has a probability~$\pmeas(E)$. If we want to know the
probability~$\pmeas(E)$, we could run $N$ independent trials. Let $x_{i}$ denote
whether the event~$E$ occurs in the $i$-th trial or not, then $\pmeas(E)$ could
be approximated to given accuracy by the relative
frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability converging to one as
$N$ goes to infinity. This fact is called the law of large
numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

>>>>

\documentclass{article}
\usepackage[ backend=biber,sorting=none]{biblatex}
\bibliography{discreteGBKS}
\usepackage{fullpage}
\usepackage{url}
\usepackage{bbm}
\usepackage{bbold}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{multicol}
\usepackage{array}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsmath}
\usepackage{wesa}
\usepackage[T1]{fontenc}
\usepackage{graphicx}

@@

\yutsung{A mathematical reason why Gleason's theorem should not be
valid in the interval-valued probability quantum mechanics. Every
classical probability measure has a one-to-one correspondence to its
Radon-Nikodym derivative. The Radon-Nikodym theorem extends to Gleason's
theorem in quantum, while the role of Radon-Nikodym derivative is
replaced by the density matrix. If there is no easy Radon-Nikodym
theorem for classical interval-valued probability measure, it is natural
that there is no easy Gleason's theorem for quantum interval-valued
probability measure...

@@

In previous section, the probability~$\pmeas(E)$ of each event~$E$
is known a priori. In reality, although the exact value of $\pmeas(E)$
may not be known, we could still assume each event has a probability.
If we want to know its value, we can run $N$ independent trials.
Let $x_{i}$ denote whether the event~$E$ occurs in the $i$-th
trial or not, then $\pmeas(E)$ could be approximated to given accuracy
by the relative frequency~$\frac{1}{N}\sum_{i}x_{i}$ with the probability
converging to one as $N$ goes to infinity. This fact is called the
law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.
